---
title: "Project 3: happypackage"
author: "Wendong Yao"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{happypackage Tutorial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(happypackage)
```

# Introduction

This package is generated for the courese STAT 302 as project 3 in University of Washington. The package includes four functions: `my_t_test`, `my_lm`, `my_knn_cv`, and `my_rf_cv`.  
`my_t_test` performs a one sample t-test in R.
`my_lm` fits a linear model in R.
`my_knn_cv`  performs a k-Nearest Neighbors Cross-Validation in R.
`my_rf_cv` performs a Random Forest Cross-Validation in R.
\n

# Tutorial

## 1. *my_t_test tutorial*
### alternative: two.sided
  \begin{align}
  H_0: \mu &= 60,\\
  H_a: \mu &\neq 60.
  \end{align}
```{r}
data("my_gapminder")
my_t_test(my_gapminder$lifeExp, mu = 60, alternative = "two.sided")
```
The p-value here is 0.09322877, which is larger than 0.05. So we cannot conclude that a significant difference exists, and we fail to reject the null hypothesis.
  
### alternative: less
```{r}
my_t_test(my_gapminder$lifeExp, mu = 60, alternative = "less")
```
The p-value here is 0.04661438, which is smaller than 0.05. So we can conclude that a significant difference exists, and we reject the null hypothesis.
  
### alternative: greater
```{r}
my_t_test(my_gapminder$lifeExp, mu = 60, alternative = "greater")
```
The p-value here is 0.9533856, which is larger than 0.05. So we cannot conclude that a significant difference exists, and we fail to reject the null hypothesis.
  

## 2. *my_lm tutorial*

