---
title: "Project 3: happypackage"
author: "Wendong Yao"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{happypackage Tutorial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(happypackage)
library(ggplot2)
library(tidyverse)
```

# Introduction

This package is generated for the courese STAT 302 as project 3 in University of Washington. The package includes four functions: `my_t_test`, `my_lm`, `my_knn_cv`, and `my_rf_cv`.  
`my_t_test` performs a one sample t-test in R.
`my_lm` fits a linear model in R.
`my_knn_cv`  performs a k-Nearest Neighbors Cross-Validation in R.
`my_rf_cv` performs a Random Forest Cross-Validation in R.
\n

# Tutorial

## 1. *my_t_test tutorial*
### alternative: two.sided
  \begin{align}
  H_0: \mu &= 60,\\
  H_a: \mu &\neq 60.
  \end{align}
```{r}
data("my_gapminder")
my_t_test(my_gapminder$lifeExp, mu = 60, alternative = "two.sided")
p_val <- my_t_test(my_gapminder$lifeExp, mu = 60, alternative = "two.sided")$p_val
```
The p-value here is `r p_val`, which is larger than 0.05. So we cannot conclude that a significant difference exists, and we fail to reject the null hypothesis.
  
### alternative: less
  \begin{align}
  H_0: \mu &= 60,\\
  H_a: \mu &< 60.
  \end{align}
```{r}
my_t_test(my_gapminder$lifeExp, mu = 60, alternative = "less")
p_val_2 <- my_t_test(my_gapminder$lifeExp, mu = 60, alternative = "less")$p_val
```
The p-value here is `r p_val_2`, which is smaller than 0.05. So we can conclude that a significant difference exists, and we reject the null hypothesis.
  
### alternative: greater
  \begin{align}
  H_0: \mu &= 60,\\
  H_a: \mu &> 60.
  \end{align}
```{r}
my_t_test(my_gapminder$lifeExp, mu = 60, alternative = "greater")
p_val_3 <- my_t_test(my_gapminder$lifeExp, mu = 60, alternative = "greater")$p_val
```
The p-value here is `r p_val_3`, which is larger than 0.05. So we cannot conclude that a significant difference exists, and we fail to reject the null hypothesis.
  

## 2. *my_lm tutorial*

```{r}
# load gapminder data
data("my_gapminder")
# use my_lm to model
lm_test <- my_lm(formula = lifeExp ~ gdpPercap + continent, data = my_gapminder)
summary(lm_test)
```

According to the summary, the p value is less than 0.05, so we reject the null hypothesis. Therefore, the slope of the linear regression line is other than 0.

```{r fig1, fig.height = 4, fig.width = 6}
# extract the intercepts
my_coef <- lm_test[, 1]
my_matrix <- model.matrix(lifeExp ~ gdpPercap + continent, 
                          data = my_gapminder)
# calculate the fitted value 
y_hat <- my_matrix %*% as.matrix(my_coef)
# create data frame for the dot plot
lm_data <- data.frame("Actual" = my_gapminder$lifeExp,
                      "Fitted" = y_hat,
                      "Continent" = my_gapminder$continent)
# draw the dot plot
lm_plot <- ggplot(lm_data, aes(x = Actual, y = Fitted, color = Continent)) +
  geom_point() +
  theme_bw(base_size = 12) +
  labs(title = "Fitted life Expectancy VS Actual life Expectancy") + 
  theme(plot.title = element_text(hjust = 0.5,
                                  face = "bold",
                                  size = 12)) +
  geom_abline(slope = 1, intercept = 0, col = "red", lty = 2)
lm_plot
```

According to the graph, we can see that the model fits all continents well, except Africa.  
While Europe has the overall highest life expectancy, following by Americans and Asia.

## 3. *my_knn_cv tutorial*

```{r}
# create an empty matrix to record the training misclassification rate and the CV misclassification rate
result <- matrix(NA, nrow = 2, ncol = 10)
# iterate from k_nn=1,…,10 and store the training misclassification rate and the CV misclassification rate
for(i in 1:10) {
  test_i <- my_knn_cv(my_gapminder, my_gapminder$continent, i, 5)
  result[1, i] <- test_i$cv_error
  accuracy <- function(x){sum(diag(x)/(sum(rowSums(x)))) * 100}
  tab_i <- table(test_i$class, my_gapminder$continent)
  training_set_error_k_nn <- round((100 - accuracy(tab_i)) / 100, digit = 2)
  result[2, i] <- training_set_error_k_nn
}
# provide row and column name for the matrix 
rownames(result) <- c("cv_err", "train_err")
colnames(result) <- paste("knn_", seq(1:10), sep = "")
a <- result[1,] - result[2,]
# print the matrix
result
```

I would choose knn = 1 model because it has the smallest training misclassification rates.  
I would choose knn = 10 model because it ahs the smallest CV misclassification rates.
I would choose knn = 10 in practice because its difference between cv error and training error is smallest.

The process of cross-validation is that, it splits the data into k folds, and repeats choosing one fold as test data while others become training data. After each fold appeared as test data, it calculates the average of mean squared error.  

It is useful because it makes the model more specific but not overfitted.

## 4. *my_rf_cv tutorial*
